Chemically Dependent Selectivity in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-20 Ben_Manuscripts/transport/Outline.tex
Figure improvements + outline additions

  We need highly selective membranes in order to perform efficient separations.

  H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
  sized pores and have the potential to disrupt conventional membrane separation
  techniques by being selective based not only on size and charge, but on chemical
  functionality as well.

  We can only learn so much from experiment. MD can give us mechanistic insights with
  atomistic resolution so that we can intelligently design new membranes for 
  solute-specific separations.

  In previous work, we determined the most likely structure of the hexagonal phase 
  formed by the monomer Na-GA3C11.
  \begin{itemize}
  	\item We developed techniques for equilibrating the hexagonal phase made by
	neat monomer as well as with varying amounts of water in the pores.
  \end{itemize}

@@

  %BJC1: copied from discussion. Need to work this in the right place
  \begin{itemize}  
  	\item Membranes, including that studied here, are often characterized 
  	with size-exclusion experiments which emphasizes selectivity based on the ability
  	to enter a given pore. 
  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
  	becomes of secondary importance since the primary purpose of these membranes is to 
  	separate molecules whose sizes are on the same order as water.
  	\item In order to handle complex waste streams with molecules of similar size,
  	it is important to take advantage of material properties other than pore size. 
  \end{itemize}

@@

@@

  Using our procedure we found that sodium ions in a solution of tip3p water
  coordinate with an average of 3.4 water molecules.
  \begin{itemize}
    \item We created a 4 x 4 x 4 nm cubic box of water with the GROMACS tool,
    \texttt{gmx solvate}
    \item We used \texttt{gmx genion} to replace water molecules with sodium
    and chloride ions in order to create a 0.6 M NaCl solution.
    \item We let the system simulate for 5 ns and reported the average
    number of coordinated water molecules per frame after discarding the first ns of 
    simulation. % need to actually do this
    \item We found that the reported average value is not sensitive to NaCl
    concentration (See section~\ref{S-section:coord_number} of the SI)
  \end{itemize}

@@

  \subsection*{Transport of Diols, Triols and Sugars}  % polyols instead of sugars?

@@

  Transport is both facilitated and hindered by additional solute hydroxyl groups
  due to their influence on radial density and hydrogen bond frequency.  	
  \begin{itemize} 
    \item Extra hydroxyl groups cause solutes to favor the water-rich pore region.
    where there is the least hindrance to movement (See Figure~\ref{fig:polyols_rdf}).
    \item Tetrose, ribose and glycerol are densest close to the pore center. This is 
    likely a result of their hydrophilicity and large size which prevents them from
    partitioning into the head group region.
    \item However, these extra hydroxyl groups facilitate a larger number of 
    hydrogen bond interactions that work to hold solutes in place (See Figure~\ref{fig:multi_hbonds}).
    \item It has been observed that hydrogen bonding in a system will generally
    reduce diffusivity~\cite{srinivas_computer_1999}
%    \item Ethylene glycol, the fastest solute in this grouping (and second fastest
%    overall), obtains the best balance of both effects.
  \end{itemize}

  The number of hydrogen bonding interactions between solutes and head groups
  increases with the number of solute hydroxyl groups.
  \begin{itemize}
    \item These solutes frequently undergo simultaneous hydrogen bond interactions as
    shown in Figure~\ref{fig:multi_hbonds}. 
    \item For example, both hydroxyl groups of ethylene glycol can undergo hydrogen
    bonds with different hydrogen bond acceptors at the same time.
    \item In some cases, all 4 hydroxyl groups of ribose are hydrogen bonded to monomer
    head groups simultaneously.
    \item Hydrogen bonds act as a kind of molecular glue which holds solutes in place, 
    especially when there are many, however proximity to the pore center partially 
    compensates for this effect in the cases of glycerol and tetrose.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  % BJC: This might be better cut off at y ~ 0.6 and then provide an inset with full RDFs
  \includegraphics[width=\linewidth]{polyols_rdf.pdf}
  \caption{}\label{fig:polyols_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{multi_hbonds.pdf}
  \caption{}\label{fig:multi_hbonds}
  \end{subfigure}
  % BJC: this subfigure is probably best suited for the supporting information.
%  \begin{subfigure}{\textwidth}
%  \centering
%  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
%  \caption{}\label{fig:dwell_hop_PG_GCL}
%  \end{subfigure}
  \caption{(a) Glycerol, tetrose and ribose are densest close to the pore center because
  they have a high number of hydrophilic groups and are relatively large. Ethylene glycol
  and propylene glycol are densest close to the head group region. (b)The number of 
  hydrogen bond interactions between solutes and monomers increases as solutes gain additional
  hydroxyl groups. Often, multiple hydroxyl groups within a solute often hydrogen bond in
  different locations simultaneously. Occasionally, all four hydroxyl groups
  of Ribose (n = 4) are involved in a hydrogen bond interaction at the same time.}\label{fig:multi_hbonds}
  \end{figure}

  Of the two diols, ethylene glycol moves significantly faster than propylene glycol
  due to propylene glycol's affinity for the monomer head groups.  
  \begin{itemize}
    \item Combined with an increase in size, the addition of a single methyl group to ethylene glycol
    increases propylene glycol's hydrophobic character and causes it to favor positions
    near monomer head groups.
    \item Both diols have comparable densities close to the pore center, however propylene glycol's
    density has a large peak near the monomer head groups relative to ethylene glycol.
    \item Propylene glycol can form more highly stablized hydrogen bonds with carboxylate groups,
    explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
    \item These observations are further reflected in its dwell and hop length distributions
    (See Figure~\ref{fig:dwell_hop_PG_GCL}).
    \item Propylene glycol exhibits longer dwell times and a narrower distribution of 
    hop lengths than ethylene glycol. 
    \item Somewhat counterintuitively, there is a relatively high density of ethylene
    glycol molecules beyond the head group region probably due to its relatively small size.
    This likely contributes to the somewhat large error bars on its MSD in Figure~\ref{fig:msds}. 
    %BJC: can show figure of radial density colored with hop lengths
    \item This implies that hops performed by ethylene glycol must be considerably larger
    than those by propylene glycol in order to result in consistently larger MSD values.
  \end{itemize}

@@

  The 4 ketone-like molecules tested show a surprising range of transport behaviors.
  \begin{itemize}
    \item Urea, acetic acid, acetamide and acetone are all characterized by a carbonyl group
    with two attached heavy atoms. 
    \item All are similar in size and are planar molecules due to the sp2 hybridization of
    their carbonyl group.
    \item The fastest solute of this grouping, acetic acid (comparable to urea), is about
    3 times faster than the slowest, acetone, but only about 10 \% smaller.
  \end{itemize}

@@

  \noindent The amides, urea and acetamide, hydrogen bond with head groups relatively 
  infrequently, but regularly coordinate with sodium ions (See Figure~\ref{fig:ketones}).
  \begin{itemize}
    \item In an average frame, acetic acid participates in more than 12 hydrogen 
    bonds with monomer head groups while urea and acetamide participate in less than 2.
    \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
  	\item Given their lower propensity to hydrogen bond one might expect amides to partition
  	out of the pore and/or to move through the pore quickly, perhaps faster than methanol.
    \item The peaks in their radial density are still situated between the pore center and the
    head groups, but closer to the pore center than other solutes that hydrogen bond with 
    carboxylate groups (see Figure~\ref{fig:simple_alcohol_rdf}, for example).
    \item Both solutes spend about half of their time with their carbonyl oxygen atom 
    coordinated to a sodium ion which restrains the solutes to within the pore region
    %BJC: it's possible the solutes hop from sodium to sodium quickly meaning solutes are not always immobilized.
    %BJC: could look into lifetime of association
    \item Interestingly, only the carbonyl oxygen atoms coordinate with sodium ions. 
    The nitrogen atoms dooes not coordinate at all despite a similar negative partial
    charge. The attached hydrogen atoms may shield this interaction.
  \end{itemize}

  \noindent Acetone has the lowest MSD of this set because it is primarily trapped near and behind 
  the head groups.
  \begin{itemize}
    \item On average, acetone coordinates with sodium with the same frequency as acetic acid 
    \item However, acetic acid spends more time in the pore center and therefore encounters
    more sodium ions.
    \item When an acetone molecule coordinates with a sodium ion, its polarity is 
    largely neutralized and it retreats towards the head group region where it can easily
    get trapped.
    \item Acetic acid and the amides have other, unoccupied, hydrophilic groups while bound
    to sodium ions which increases their stability in the pore.
  \end{itemize}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_rdf.pdf}
  \caption{}\label{fig:ketones_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}
  \caption{}\label{fig:ketone_hbonds}
  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{ketone_ratio.pdf}
%  \caption{}\label{fig:ketones_ratio}
%  \end{subfigure}
  \caption{(a) The radial density near the pore center (r = 0) decreases
  with decreasing solute MSD. (b) The amides hydrogen bond with water far
  less than acetic acid, however they tend to coordinate with sodium ions
  more frequently.}\label{fig:ketones}
  \end{figure}

@@

  We also studied the transport properties of sulfur analogs of glycerol, ethylene
  glycol and acetone.
%  Finally, we studied the transport properties of sulfur-containing compounds similar
%  to some of the solutes studied above.
  \begin{itemize}
    \item We replaced all but one oxygen atom of ethylene glycol and glycerol with sulfur atoms
    to create Dimercaptoethanol and 2,3-Dimercapto-1-propanol.
    \item We replaced the carbonyl carbon of acetone with sulfur in order to create DMSO. 
  	\item Sulfur is unable to hydrogen bond, however it is soluble in water  %BJC: maybe a reference to why sulfur can't hbond
 \end{itemize}

%  	\item Comparisons of their RDFs are shown in Figure~\ref{fig:sulfur_analog_rdfs}.
%  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
  \caption{}\label{fig:SOH_GCL_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMS.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \caption{(a) The RDF of mercaptoethanol is similar to ethylene glycol except 
  for its higher density in the tail region. (b) 2,3-Dimercapto-1-propanol is
  densest near the pore wall, unlike glycerol whose density is very high in the pore
  center. (c) Dimethylsulfoxide has a higher density than acetone close to the pore
  center which may in part explain its marginally larger MSD.}\label{fig:sulfur_analog_rdfs}
  \end{figure}

  \noindent Mercaptoethanol has a similar average MSD and RDF to ethylene glycol.
  \begin{itemize}
    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
    \item Some of this can be accounted for by the higher density of mercaptoethanol 
    molecules in the head group / tail region, where transport is inherently slower. 
    \item There are nearly 40 \% more mercaptoethanol molecules than ethylene 
    glycol molecules beyond 0.8 nm from the pore center. 
    \item Conversely, mercaptoethanol exhibits some of the highest single solute MSDs 
    (See Figure~\ref{fig:SOH_trace})  % Only methanol has greater (I think)
    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
    \item This may lead to larger hops in the pore region.
%    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
%    monomer head group simultaneously,
%    \item Less frequent hydrogen bonding and an affinity for the pore region may be
%    responsible for these hops.
  \end{itemize}

@@

  \noindent 2,3-Dimercapto-1-propanol exhibits slower transport than glycerol because it spends more time
  near monomer head groups. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
  \begin{itemize}
    \item Glycerol frequently hydrogen bonds with more than one head group at a time (See Figure~\ref{fig:multi_hbonds}).
    % BJC: can probably quantify the following:
    \item It can also hydrogen bond with water molecules which increases its stability
    in the pore region.
    \item 2-3-Dimercapto-1-propanol preferentially hydrogen bonds with head groups 
    so it gravitates towards the head group region.
  \end{itemize}

  \noindent DMSO has a comparable if not larger MSD than acetone even though it
  is a slightly larger molecule.
  \begin{itemize}
    \item The radial density of DMSO is higher than acetone close to the pore center.
  	\item The pyramidal structure of DMSO may force it to spend more time closer to
  	the pore center.
  	%BJC: quantify sodium coordination O group of DMSO
  \end{itemize}

  \subsection*{Hydrogen bond acceptors}  % Need a better heading since all molecules in this study are acceptors

  %BJC: should probably at least mention acetone again in this section  
  The slowest set of molecules we studied can accept hydrogen bonds, but cannot donate
  them. 
  \begin{itemize}
  	\item Among this set are the two slowest solutes in our study: Tetrahydrofuran and Dimethyl Formamide.
  	\item The MSDs of ethyl acetate, propylene carbonate and acetone are only marginally larger.
  	% EAC and PCB are both larger molecules. Acetone is small. %BJC: not sure how far I should dive into this point
  \end{itemize}

@@

  \noindent The radial density of solutes near the pore center in this set is surprisingly high
  as shown in Figure~\ref{fig:nondonors_rdf}.
  \begin{itemize}
    \item Propylene carbonate and ethyl acetate are among the largest solutes
    in this study. Their size prevents them from easily entering the tail 
    region and generally gives faster transport properties since they spend
    more time in the pore region. 
    \item However, this is not a hard rule. When a solute does overcome the 
    barrier of entry beyond the head group region, it can become trapped. All
    solutes in this set show a peak $\geq$ 1 nm from the pore center which is
    likely caused by solutes that get trapped in the tail region for a significant
    amount of time.
	\item The peak density of THF is considerably offset from the pore center.
	\item Observations of single THF trajectories have revealed that it does not make
	large hops while in the pore center.
	\item THF becomes nearly immobilized while associated with sodium ions (See 
	Figure~\ref{fig:thf_sodium_coordination}).
	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
	higher than THF near the head groups. The planar shape of DMF causes it to 
	become stuck between head groups. Excursions into the pore region do not
	necessarily result in large hops.
  \end{itemize}

  \noindent Carbonyl groups continue to show high degrees of association with sodium ions. 
  \begin{itemize}
    \item The number of sodium ions coordinated to the carbonyl group of 
    propylene carbonate, dimethyl formamide, ethyl acetate are consistent with 
    that shown by acetone, all between 6 and 7 per frame (See 
    figure~\ref{fig:nondonors_hbonds})
    \item The carbonyl group of the amides studied in the previous section
    associate with sodium nearly twice as frequently as compounds that don't
    contain nitrogen (see figure~\ref{fig:ketone_hbonds}).
    \item In all cases, other polar groups on carbonyl-containing compounds
    associate with sodium in negligible amounts.
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nondonors_rdf.pdf}
  \caption{}\label{fig:nondonors_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nondonor_hbonds.pdf}
  \caption{}\label{fig:nondonors_hbonds}
  \end{subfigure}
  \end{figure}

>>>>

  We need highly selective and permeable membranes in order to perform efficient 
  separations.
  \begin{itemize}
    \item Cleanup of fracking water
    \item Removal of organic micropollutants, such as pesticides, pharmaceuticals,
    and personal care products, from the drinking water supply.
    \item Desalination
    \item All of these separations are possible with current commercial membrane
    separation techniques but they are too energy intensive to be worth the 
    capital investment needed to start the processes.
  \end{itemize}

  Nanostructured membranes offer the potential for molecular-level design which
  could overcome the limitations faced by conventional membrane technologies.
  \begin{itemize}
    \item Mitigation of stochastic aspects of membrane synthesis
    \item Well-defined and uniform pores increase selectivity
    \item Solute-specific separations.
  \end{itemize}

  H\textsubscript{II} phase lyotropic liquid crystals have densely packed, uniform
  sized pores and have the potential to disrupt conventional membrane separation
  techniques by being selective based not only on solute size and charge, but on 
  chemical functionality as well.
  \begin{itemize}
    \item Uniform pores lead to high selectivity
    \item The hexagonal geometry is ideal for high permeability
  \end{itemize}

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. 
  \begin{itemize}
  	\item The separation performance of these membranes has been primarily 
  	characterized with size-exclusion experiments which emphasizes selectivity
  	based on the ability to enter a given pore. 
  	\item While size-exclusion is a useful separation, it cannot 
  	reliably purify a solution where the solute size is on the same order as water.
%  	\item Once on the nm to sub-nm pore size regime, size-exclusion 
%  	becomes of secondary importance since the primary purpose of these membranes is to 
%  	separate molecules whose sizes are on the same order as water.
%  	\item In order to handle complex waste streams with molecules of similar size,
  	\item Therefore, it is important to take advantage of material properties other
  	than pore size.
  	\item Unfortunately, the complexity of LLC Membranes has obscured the interpretation 
  	of experimental transport studies.
  \end{itemize}

  Molecular dyanmics (MD) simulation can give us mechanistic insights with atomistic
  resolution so that we can directly observe small solute transport within LLC membrane
  nanopores and intelligently design new membranes for solute-specific separations.

  In our previous work, we determined the most likely structure of the hexagonal phase 
  formed by the monomer Na-GA3C11.
  \begin{itemize}
  	\item We developed techniques for equilibrating the hexagonal phase made by
	neat monomer as well as with varying amounts of water in the pores.
  \end{itemize}

@@

@@

  In all RDF plots, we include the average RDF of the head groups as a reference.
  \begin{itemize}
    \item The head group RDF shown is the average of the head group RDFs for each
    solute system in the plot.
    \item We generated 95 \% confidence intervals by bootstrapping the frame-by-frame
    RDFs obtained from both systems.
  \end{itemize}

@@

  Using our procedure we found that sodium ions in a solution of tip3p water
  coordinate with an average of 3.6 water molecules.
  \begin{itemize}
    \item We created a 4 x 4 x 4 nm cubic box of water with the GROMACS tool,
    \texttt{gmx solvate}
    \item We used \texttt{gmx genion} to replace water molecules with sodium
    and chloride ions in order to create a 0.1 M NaCl solution.
    \item We let the system simulate for 5 ns and reported the average
    number of coordinated water molecules per frame after discarding the first ns of 
    simulation. % need to actually do this
    % BJC1: NaCl starts to crystallize for higher concentrations leading to lower coordination numbers
%    \item We found that the reported average value is not sensitive to NaCl
%    concentration (See section~\ref{S-section:coord_number} of the SI)
  \end{itemize}

@@

  \subsection*{Transport of Diols, Triols and Sugars}\label{section:polyols}

@@

  Transport is both facilitated and hindered by additional solute hydroxyl groups
  due to their influence on radial density and hydrogen bond frequency.  	
  \begin{itemize} 
    \item Extra hydroxyl groups cause solutes to favor the water-rich pore region.
    where there is the least hindrance to movement (See Figure~\ref{fig:polyols_rdf}).
    \item Tetrose, ribose and glycerol are densest close to the pore center. This is 
    likely a consequence of both their hydrophilicity and large size which prevents
    them from partitioning into the head group region.
    \item However, these extra hydroxyl groups facilitate a larger number of 
    hydrogen bond interactions that work to hold solutes in place (See Figure~\ref{fig:multi_hbonds}).
    \item It has been observed that hydrogen bonding in a system will generally
    reduce diffusivity~\cite{srinivas_computer_1999}
%    \item Ethylene glycol, the fastest solute in this grouping (and second fastest
%    overall), obtains the best balance of both effects.
  \end{itemize}

  The number of hydrogen bonding interactions between solutes and head groups
  increases with the number of solute hydroxyl groups.
  \begin{itemize}
    \item These solutes frequently undergo simultaneous hydrogen bond interactions as
    shown in Figure~\ref{fig:multi_hbonds}. 
    \item For example, both hydroxyl groups of ethylene glycol can undergo hydrogen
    bonds with different hydrogen bond acceptors at the same time.
    \item In some cases, all 4 hydroxyl groups of ribose hydrogen bonded to monomer
    head groups simultaneously.
    \item Hydrogen bonds act as a kind of molecular glue which holds solutes in place, 
    especially when there are many, however proximity to the pore center partially 
    compensates for this effect in the cases of glycerol and tetrose, causing them to
    have relatively high MSDs for their size.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  % BJC: This might be better cut off at y ~ 0.6 and then provide an inset with full RDFs
  \includegraphics[width=\linewidth]{polyols_rdf.pdf}
  \caption{}\label{fig:polyols_rdf}
  \end{subfigure}
  \begin{subfigure}{0.50\textwidth}
  \vspace{-0.275cm}
  \includegraphics[width=\linewidth]{multi_hbonds.pdf}
  \caption{}\label{fig:multi_hbonds}
  \end{subfigure}
  % BJC: this subfigure is probably best suited for the supporting information.
%  \begin{subfigure}{\textwidth}
%  \centering
%  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
%  \caption{}\label{fig:dwell_hop_PG_GCL}
%  \end{subfigure}
  \caption{(a) Glycerol, tetrose and ribose are densest close to the pore center because
  they have a high number of hydrophilic groups and are relatively large. Ethylene glycol
  and propylene glycol are densest close to the head group region. (b) The number of 
  hydrogen bond interactions between solutes and monomers increases as solutes gain additional
  hydroxyl groups. The number of hydrogen bonds made by a single solute in different locations
  simultaneously, n, also increases with the number of hydroxyl groups. In the most extreme case,
  all four hydroxyl groups of Ribose (n = 4) are involved in a hydrogen bond interaction at
  the same time.}\label{fig:multi_hbonds}
  \end{figure}

  Of the two diols, ethylene glycol moves significantly faster than propylene glycol
  due to propylene glycol's affinity for the monomer head groups.  
  \begin{itemize}
    \item Combined with an increase in size, the addition of a single methyl group to ethylene glycol
    increases propylene glycol's hydrophobic character and causes it to favor positions
    near monomer head groups.
    \item Both diols have comparable densities close to the pore center, however propylene glycol's
    density has a large peak near the monomer head groups relative to ethylene glycol.
    \item Propylene glycol can form more highly stabilized hydrogen bonds with carboxylate groups,
    explaining the higher incidence of hydrogen bonds shown in Figure~\ref{fig:multi_hbonds}.
%    \item These observations are further reflected in its dwell and hop length distributions
%    (See Figure~\ref{fig:dwell_hop_PG_GCL}).
%    \item Propylene glycol exhibits longer dwell times and a narrower distribution of 
%    hop lengths than ethylene glycol. 
    \item Somewhat counterintuitively, there is a relatively high density of ethylene
    glycol molecules beyond the head group region probably due to its relatively small size.
    This likely contributes to the somewhat large error bars on its MSD in Figure~\ref{fig:msds}. 
    %BJC: can show figure of radial density colored with hop lengths
    \item This implies that hops performed by ethylene glycol must be considerably larger
    than those by propylene glycol in order to result in consistently larger MSD values.
  \end{itemize}

@@

  The 4 ketone-like molecules tested show a surprising range of transport behaviors.
  \begin{itemize}
    \item Urea, acetic acid, acetamide and acetone are all characterized by a carbonyl group
    with two attached heavy atoms. 
    \item All are similar in size and are planar molecules due to the sp2 hybridization of
    their carbonyl group.
    \item The fastest solutes of this grouping, acetic acid and urea, are about
    3 times faster than the slowest, acetone. %, but only about 10 \% smaller.
  \end{itemize}

@@

  \noindent The amides, urea and acetamide, hydrogen bond with head groups relatively 
  infrequently, but regularly coordinate with sodium ions (See Figure~\ref{fig:ketones}).
  \begin{itemize}
    \item In an average frame, acetic acid participates in more than 12 hydrogen 
    bonds with monomer head groups while urea and acetamide participate in less than 2.
    \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity. % citation
  	\item Given their lower propensity to hydrogen bond one might expect amides to partition
  	out of the pore and/or to move through the pore quickly, perhaps faster than methanol.
    \item Both RDFs contain peaks in their radial density that are situated between the 
    pore center and the head groups, but closer to the pore center than other solutes that
    hydrogen bond with carboxylate groups.
    \item Solutes that hydrogen bond frequently tend to show peaks in their RDFs near 
    0.5-0.6 nm from the pore center (see Figure~\ref{fig:simple_alcohol_rdf}, for example) 
    and those that coordinate with sodium ions more frequently tend to show peaks in
    their RDFs near 0.2-0.3 nm from the pore center.
    \item Both solutes spend about half of their time with their carbonyl oxygen atom 
    coordinated to a sodium ion which restrains the solutes to within the pore region
    \item Only the carbonyl oxygen atoms coordinate with sodium ions. 
    The nitrogen atoms do not coordinate at all despite a similar negative partial
    charge because the attached hydrogen atoms shield this interaction by making the
    NH\textsubscript{2} group approximately neutral.
  \end{itemize}

  \noindent Acetone has the lowest MSD of this set because it either coordinates with
  sodium or stays trapped near and behind the head groups.
  \begin{itemize}
    \item On average, acetone coordinates with sodium with the same frequency as acetic acid 
    which is manifested as a peak in its RDF about 0.2 nm from the pore center.
    \item However, acetic acid spends more time in the pore center and therefore encounters
    more sodium ions.
    \item When an acetone molecule coordinates with a sodium ion, its polarity is 
    largely neutralized and it retreats towards the head group region where it can easily
    get trapped.
    \item Acetic acid and the amides have other, unoccupied, hydrophilic groups while bound
    to sodium ions which increases their stability in the pore.
  \end{itemize}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_rdf.pdf}
  \caption{}\label{fig:ketones_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ketone_hbonds.pdf}
  \caption{}\label{fig:ketone_hbonds}
  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{ketone_ratio.pdf}
%  \caption{}\label{fig:ketones_ratio}
%  \end{subfigure}
  \caption{(a) The radial density near the pore center (r = 0) decreases
  with decreasing solute MSD. Peaks in the RDFs of urea, acetamide and
  acetone near 0.2 - 0.3 nm from the pore center are likely due to coordination
  with sodium ions. (b) The amides hydrogen bond with water far less than 
  acetic acid, however they tend to coordinate with sodium ions more 
  frequently.}\label{fig:ketones}
  \end{figure}

@@

  We also studied the transport properties of sulfur analogs of glycerol, ethylene
  glycol and acetone.
  \begin{itemize}
    \item We replaced all but one oxygen atom of ethylene glycol and glycerol with sulfur atoms
    to create dimercaptoethanol and 2,3-dimercapto-1-propanol.
    \item We replaced the carbonyl carbon of acetone with sulfur in order to create DMSO. 
  	\item Sulfur is unable to hydrogen bond making thiols less soluble in water than
  	their hydroxyl group analogs.  % citation
 \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
  \caption{}\label{fig:SOH_GCL_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMS.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \caption{(a) The RDF of mercaptoethanol is similar to ethylene glycol except 
  for its higher density in the tail region and consequently lower density in the
  pore region. (b) 2,3-dimercapto-1-propanol is densest near the head groups, 
  unlike glycerol whose density is very high close to the pore center. 
  (c) Overall, dimethylsulfoxide has a higher density than acetone within the 
  pore region which may in part explain its marginally larger MSD.}\label{fig:sulfur_analog_rdfs}
  \end{figure}

  \noindent Mercaptoethanol has a similar average MSD and RDF to ethylene glycol.
  \begin{itemize}
    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
    \item Some of this can be accounted for by the higher density of mercaptoethanol 
    molecules in the head group / tail region, where transport is inherently slower. 
    \item There are nearly 40 \% more mercaptoethanol molecules than ethylene 
    glycol molecules beyond 0.8 nm from the pore center. 
    \item Conversely, mercaptoethanol exhibits some of the highest single solute MSDs 
    (See Figure~\ref{fig:SOH_trace})  % Only methanol has greater (I think)
    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
    which may lead to larger hops when in the pore region.
    \item The range of behaviors shown by mercaptoethanol explain the large variance
    of its MSD.
%    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
%    monomer head group simultaneously,
%    \item Less frequent hydrogen bonding and an affinity for the pore region may be
%    responsible for these hops.
  \end{itemize}

@@

  \noindent 2,3-dimercapto-1-propanol exhibits slower transport than glycerol 
  because more of it partitions into the tail region. % BJC: should I give all the solutes nicknames (i.e. their residue names)?
  \begin{itemize}
    % BJC1: maybe next point better expressed as a percentage in each region.
    \item The density of glycerol is always higher up to 0.7 nm from the 
    pore center where the population of 2,3-dimercapto-1-propanol then 
    becomes more dense into the tail region. 
    \item Glycerol participates in about 3 times as many hydrogen bonds
    as 2,3-dimercapto-1-propanol. %BJC1: 52.2 / 16.4 ~= 3.2. Includes hbonds with water (recieved and donated) as well as with ether + carboxylate oxygen atoms.
    \item Because sulfur cannot hydrogen bond, 2,3-dimercapto-1-propanol is 
    less soluble than glycerol in the water-filled pores and more readily 
    partitions into the tail region.
  \end{itemize}

  \noindent DMSO has a comparable if not larger MSD than acetone even though it
  is a slightly larger molecule.
  \begin{itemize}
    \item The density of DMSO is higher than acetone in the pore region,
    except for the peak exhibited by acetone near 0.2 nm, which is due to 
    sodium ion association.
    %BJC1: better to report a percentage?
    \item On average, the 24 DMSO molecules coordinate with 8.4 sodium ions 
    per frame, compared to 6.2 per frame by acetone.
  	\item The pyramidal structure of DMSO may force it to spend more time closer to
  	the pore center which increases its interaction with sodium ions.
  	\item The tendency of DMSO to stay in the pore region counterbalances the
  	sodium ion interactions to give it a higher MSD than acetone. 
  \end{itemize}

  \subsection*{Hydrogen Bond Acceptors}  % Need a better heading since all molecules in this study are acceptors

  % BJC: should probably at least mention acetone again in this section  
  The slowest set of molecules we studied can accept hydrogen bonds, but cannot donate
  them. 
  \begin{itemize}
  	\item Among this set are the two slowest solutes in our study: Tetrahydrofuran and Dimethyl Formamide.
  	\item The MSDs of ethyl acetate, propylene carbonate and acetone are only marginally larger.
  \end{itemize}

@@

  \noindent The radial density of solutes near the pore center in this set is 
  surprisingly high as shown in Figure~\ref{fig:nondonors_rdf}.
  \begin{itemize}
    \item Propylene carbonate and ethyl acetate are among the largest solutes
    in this study. Their size prevents them from easily entering the tail 
    region and consequently gives faster transport properties 
    % since they spend more time in the pore region. 
    \item However, this is not a hard rule. When a solute does overcome the 
    barrier of entry beyond the head group region, it can become trapped. All
    solutes in this set show at least a small peak $\geq$ 0.9 nm from the pore 
    center which is likely caused by solutes that get trapped in the tail region
    for a significant amount of time.
  \end{itemize}

  \noindent Solutes do not make frequent hops while in the pore region.
  \begin{itemize}
	\item Observations of single THF trajectories have revealed that it becomes 
	nearly immobilized while associated with sodium ions 
	(See Figure~\ref{fig:thf_sodium_coordination}).
	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
	higher than THF near the head groups. The planar shape of DMF causes it to 
	become stuck between head groups. Excursions into the pore region do not
	necessarily result in large hops.
  \end{itemize}

  \noindent Carbonyl groups continue to show high degrees of association with
  sodium ions. 
  \begin{itemize}
    \item The number of sodium ions coordinated to the carbonyl group of 
    propylene carbonate, dimethyl formamide, ethyl acetate are consistent with 
    that shown by acetone, all between 6 and 7 per frame (See 
    figure~\ref{fig:nondonors_hbonds})
    \item The carbonyl group of the amides studied in the previous section
    associate with sodium nearly twice as frequently as compounds that don't
    contain nitrogen (see figure~\ref{fig:ketone_hbonds}).
%    \item In all cases, other polar groups on carbonyl-containing compounds
%    associate with sodium in negligible amounts.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nondonors_rdf.pdf}
  \caption{}\label{fig:nondonors_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nondonor_hbonds.pdf}
  \caption{}\label{fig:nondonors_hbonds}
  \end{subfigure}
  \caption{(a) The radial density of solutes that can only receive hydrogen bonds
  is surprisingly high in the pore region. Conversely, there is also an appreciable
  amount of each solute in the tails. (b) The low MSDs exhibited by each of these
  solutes is due to a combination of entrapment within the tail region and a high 
  degree of coordination with sodium ions.}\label{fig:nondonors}
  \end{figure}
